Results

### 2021-12-07 Manuscript/Manuscript_Discussion.Rmd
including Tjibbe's review

We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.\
By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
Our tool consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e. Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\ 
The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the online database in terms of traffic and download quota.\
The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].

@@

One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\
This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
the hyperparamer evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

@@

The field of literature review automatisation is mature and ripe with innovation, and we expect an increasing use of such technologies to confront the ever-faster production of scientific literature.
We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
We tried to contribute to the field with an innovative methodology and tool that provides excellent performance and easy integration with existing systematic review pipelines.
The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of solutions we developed to solve various SRA issues and that can be used to improve existing solutions.

>>>>

We propose a new integrated framework to help researchers collect and screen scientific publications characterised by high performance and versatility, joining the growing field of systematic review automation (SRA) and helpers (SRH) tools [@cohen2006reducing; @cohen2010evidence; @ananiadou2009supporting; @o2015using].
This framework joins standard approaches and uses ad-hoc solutions to deal with common SRA issues.
By freely sharing the tool as an open-source R package and by following a modular design, we tried to adopt some of the so-called Vienna Principles advocated by the International Collaboration for the Automation of Systematic Reviews (ICASR) [@beller2018making].\
The framework consists of four main components: 1) an integrated query-based citation search and management engine, 2) a text-to-feature extractor module, 3) a Bayesian active machine learning-based citation classifier, and 4) a data-driven search query generation algorithm.\

The framework's search engine module is capable of automatically collecting citation data from three well-known scientific databases (i.e. Pubmed, Web of Science, and the database of the Institute of Electrical and Electronics Engineers) as well as process manually downloaded results from both the mentioned and other (SCOPUS, EMBASE) databases.
In comparison, most SRH tools, commercial or free to use, rely either on internal databases (e.g., Mendeley https://www.mendeley.com/) sometimes focusing just on a particular topic [@visser2010performing] or on a single external data source [@thomas2007eppi; @poulter2008mscanner; @soto2019thalia].\
Mixing different databases is fundamental to have a more comprehensive view of the literature [@bajpai2011search; @wilkins2005embase; @woods1998medline]:
in our results, 18.7% of the positive matches found were unique for one of the different data sources, and no positive record was present in all of them (data not shown).\
The online search algorithms are efficient enough to manage tens of thousands of search results, using various expedients to overcome the limitations of the queried databases in terms of traffic and download quota.
The results are then automatically organized, deduplicated and arranged by "simple query ordering" in a uniform corpus.
The preliminary ordering allow to increase the positivity rate in the initial training set [@wallace2010active].

@@

One of the central innovations we introduced is the concept of "uncertainty zone", whose implementation is possible thanks to the Bayesian foundation of the classification model.
This construct guides the selection of the records to review, dynamically updating and shrinking after every CR iteration, as more uncertain predictions are evaluated (Supplemental Material S2 Fig. 1).\
This approach overcomes the usual requirement of dataset-specific hard thresholds in active machine learning, and also allows to review multiple items at once between iterations [@laws2008stopping; @miwa2014reducing; @zhu2010confidence].
The parameters our algorithm needs are instead quite general and non task-specific, like the PPD intervals based on which the uncertainty zone is built ,and the maximum number of iterations with no positive matches after which a session is concluded;
the hyperparameter evaluation shows that the algorithm is robust against variations in these parameters and we expect the default values to preform well on most datasets.\
Since researchers are asked to review both records with a positive predicted label and those inside the uncertainty zone, this method can be considered as a unifying synthesis of the "certainty" and "uncertainty" paradigms of active learning [@miwa2014reducing].\

@@

The field of literature review automation is maturing rapidly, and we expect an increasing use of such technologies to manage the ever-faster rate of scientific production.
We believe it is appreciable that a multiplicity of tools are being made available to let researchers and policymakers find the instrument that better fits their needs.\
We contribute to this field with an innovative framework that provide excellent performance and easy integration with existing systematic review pipelines.
The value of this work lies not only in the framework itself, which we provide as open-source software, but in the set of methodologies we developed to solve various SRA issues and that can be used to improve already existing solutions.

### 2021-12-07 Manuscript/Manuscript_Introduction.Rmd
update
including Tjibbe's review

## Introduction

@@

This is especially true for biomedical research, a trend further increased by the COVID19 pandemic, thanks to decreased journals' processing time and the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].

@@

with machine learning, such text-derived data can be used to map and reproduce human judgment, automating the citation screening [@ikonomakis2005text].
One of the most successful approaches to text screening is active machine learning:
researchers review the predictions made by the learning algorithm, focusing on the most uncertain predictions ("uncertainty" based active machine learning) or on those giving a document a higher probability of being relevant ("certainty" based active ML) [@miwa2014reducing].\
The automatisation of systematic reviews has been ripe with improvements in the last years, and it is possible to foresee that such techniques will become a standard approach [@beller2018making]. See @ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating for in-depth evaluations of research in this field.
Many of these studies have generated a set of user-friendly commercial and free-to-use tools [see @marshall2015systematic, table 1].
Despite the significant advances, each method has various shortcomings, both in usability and efficiency [@o2015using].
We tried to address some of these limitations by creating an integrated framework that tries to simplify systematic reviews in innovative ways:
we provide solutions for automatic citation collection and management from multiple online sources and a Bayesian, active machine learning-based tool to support humans in the screening task, exponentially reducing the number of records to review.
In particular, we exploit the characteristics of Bayesian analysis to overcome the shortcoming of both "certainty" and "uncertainty" based active learning and the difficulties in defining stopping rules [@miwa2014reducing].
Finally, we propose an experimental method to semi-automatically generate efficient search queries given an already labelled set of publications.\

@@

the evaluation of the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms.
The actual protocol of this systematic review is published in [@newis].\

@@

in the Result section, we show the framework outputs and performance once applied to the example topic; in the Discussion,
we lay out the methodological justification behind the different components and features of the framework.

>>>>

# Introduction

@@

This is especially true for biomedical research, a trend further increased by the COVID-19 pandemic, thanks to faster article' processing time by publishers and the diffusion of preprint databases' usage [@aviv2021publication; @horbach2020pandemic; @hoy2020rise].

@@

with machine learning, such text-derived data can be used to map and reproduce human judgment, automating the citation screening [@ikonomakis2005text].\
The automation of systematic reviews has been ripe with improvements in the last years [@ananiadou2009supporting; @o2015using; @tsafnat2013automation; @jonnalagadda2015automating], and it is possible to foresee that it is going to become the standard approach in the field [@beller2018making], with many solutions already being turned into commercial and free-to-use tools [see @marshall2015systematic, table 1].\
In this manuscript we present an open source, production-ready framework which further contributes to the state-of-the-art in systematic review automation (SRA) and helpers (SRH) tools.
We improve the "retrieval phase" by providing a unified framework for the automatic collection and management of scientific literature from multiple online sources.
For the citation screening (appraisal) phase, we built an active machine learning-based [@settles2009active, @miwa2014reducing; @miwa2014reducing] protocol, which exploits a Bayesian framework to efficiently identify potentially relevant documents that require human review while automatically screening-out the large majority of clearly non-relevant ones;
the algorithm then uses human reviews to iteratively increase classification accuracy.
Finally, we included a tool to generate new search queries given an already labelled citation data set, in order to identify relevant research possibly missed by human-made queries.\

@@

the evaluation of the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms;
the protocol is published in [@newis].\

@@

in the Result section, we show the framework outputs and performance once applied to the example topic;
in the Discussion, we lay out the methodological justification behind the different components and features of the framework.

### 2021-12-07 Manuscript/Manuscript_Methods.Rmd
including Tjibbe's review

We built an R [@rstat] based framework to simplify two aspects of systematic reviews:
record acquisition and classification.
The framework comprises several modules that communicate through intermediate outputs stored in standard formats, which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
The tasks carried out by the framework are grouped into "sessions", i.e., a set of actions that starts from a search query to obtain a set of scientific citation data (records), which are then labelled as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest (Fig. 1).
The framework can generate a new query from this labelled set and perform a new session to find records possibly missed by the first query.\
The researcher initiates the process with a starting query derived by domain knowledge from which she expects a high relevant/non-relevant record ratio.\
Follows a description of the framework's components.\

@@

We built a set of tools to let users automatically search and download citation data from three major scientific databases ("sources"):
Pubmed (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
The framework takes care of authorization management for non-open databases like WOS and IEEE.
It is also possible to download and import records in the framework manually;
this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/search/form.uri?display=basic#basic>) and EMBASE databases (<https://www.embase.com/#advancedSearch/default>), for which a comprehensive API interface was not easy to build.
An extra manual search was necessary also for Pubmed, since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
The acquired records are merged into a single database, resolving duplicates and different formatting between sources.
The records are ordered according to the frequency of the positive query terms (e.g., not preceded by a $NOT$ modifier) in the title and abstract ("simple query ordering").\
The researcher is then asked to label a number of records to create the "initial training set" needed to start the automatic classification.
We suggest manually labelling the first 250 records (see "hyperparameter optimization" later).
The simple query ordering increases the positivity rate in the initial training set [@wallace2010active], which provide higher sensitivity during automatic classification [@chawla2004special].

@@

The collected citation data have a number of fields characterizing a scientific publication.
The framework models the relevance of a record based on the following fields:
title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
A series of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
The processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), common stopwords (i.e., sentence components bringing no meaning) removal, part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatization of the terms (i.e., reduction to their base grammar form).
Text processing for authors, keywords and MESH terms identifies logical units (e.g., author's full names, composite keywords) and extracts them.\
Terms appearing in less than 5% of the labelled documents are removed from negative records.
All terms in the positive set are kept to increase sensitivity at the cost of specificity.\
Some terms tend to co-appear in records (non-consecutive ngrams, nc-ngrams), often carrying a particular meaning when copresent.
To detect nc-ngrams, we generated a word network representation [@rousseau2015graph] posing edges between terms with a cosine similarity in terms of record co-occurrence > 0.5.
We extracted the maximal cliques in the network [@eppstein2010listing] representing highly correlated groups of terms;
These groups of terms are added to the data set as individual features.
Only nc-ngrams comprising a maximum of ten terms are kept.\
A second network is built using a co-occurrence threshold of 0.9.
In this case, the cliques represent terms that always appear together and therefore can be considered redundant (i.e., they do not need to be considered separately).
These terms are merged to increase computation efficiency and reduce overfitting.\
The output is a Document-Term Matrix (DTM), with $N_d$ rows representing the records ($D_i$), $N_t$ terms column for the $t_{field}$ terms (divided by record field) and ${0,1}$ values whether $t_{field} \in D_i$.
We also enriched the DTM with features referencing the number of terms in each field to help the model scale term importance based on the field length.

@@

To assign the labels, we employed an "active learning" [@settles2009active, @miwa2014reducing] approach, where a human reviews a specific subset of predictions made from the machine, which is then retrained on the manually reviewed dataset.
This process proceeds iteratively, decreasing prediction uncertainty.\
Label assignment is done through the identification of an "uncertainty zone" whose construction is possible thanks to the Bayesian nature of BART, which provides full PPDs instead of point-wise predictions for each record.\
To describe the process formally, we define

@@

## Relevant terms' extraction

@@

Since the algorithm is data-driven, it creates queries that effectively select positive records from the input dataset but may be not specific enough once applied to actual research databases.
Therefore we appended an extra subquery in $AND$, which specifies the general topics of our search and delimitates the search domain.\
The new query was used to initiate a second search session.

@@

We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the classification model consistency (see Discussion for the theoretical justification).
The surrogate model uses as predictor the lower bound of the 98% PrI of the records' PPD with weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).\
The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r], of which we reported the posterior median and 90% Credible Interval [90% CrI].
The $R^2$ also provides an evaluation of the consistency of the original classification model.
Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing plausible worst-case scenarios.\
The surrogate model is then used to generate the predictive cumulative distribution of the number of missed positive records in the whole dataset.
This distribution allows estimating the expected total posterior "Sensitivity" and the "Work saved over random" (WSoR) of the classification model in the full (unreviewed) dataset.
The WSoR is one minus the number of records to manually label at random to find the same number of positives; this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting].\
For the number of predicted positive records, the sensitivity and the WSoR, we reported the "truncated 90% PrI" [trunc. 90% PrI], which is the uncertainty interval bounded at the number of observed total positive records (i.e., there cannot be less predicted positive records than observed).

@@

To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" made of the first 1200 records from the first session dataset.
The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole dataset got labelled.\
For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required review over the total) and "Sensitivity" (number of positive records found over the total of positives).
We then identified homogeneous "performance clusters" of scores given hyperparameter values using a partition tree [@rpart].
For the rest of the study, we used the best hyperparameter set in terms of Sensitivity followed by Efficiency from the cluster with the highest average score.

>>>>

We built an R [@rstat] based framework to simplify two aspects of systematic reviews:
record acquisition and classification.
The code used to generate the results in the manuscript is available at X while an update version of the framework is distributed as an R package at Y.
The framework includes several modules that communicate through intermediate outputs stored in standard formats, which make it possible for users to extend the framework or easily integrate it with other tools in their pipeline.
See Supplemental Material S1 for an in-depth description of the framework and how to use it.\
The tasks carried out by the framework are grouped into "sessions", which comprise obtaining scientific citation data (records) using a search query and then labelling them as relevant ("positive" in the rest of the text) or not ("negative") for the topic of interest with the help of a machine learning engine (Fig. 1).
The initial search query should be built using domain knowledge, trying to achieve a high relevant/non-relevant record ratio.\
The framework can then generate a new data-driven query from this labelled set to perform a new session to find records possibly missed by the first query.\

@@

We built a set of tools to let users automatically search and download citation data from three major scientific databases ("sources"):
Pubmed (<https://pubmed.ncbi.nlm.nih.gov/>), Web Of Science (WOS, <https://apps.webofknowledge.com/>) and the Institute of Electrical and Electronics Engineers (IEEE, <https://ieeexplore.ieee.org/Xplore/home.jsp>).
The framework takes care of authorization management for non-open databases like WOS and IEEE.
It is also possible to download and import records in the framework manually;
this is particularly useful to acquire records from the SCOPUS (<https://www.scopus.com/>) and EMBASE databases (<https://www.embase.com/>), for which a comprehensive API interface was not easy to build.
An extra manual search was necessary also for Pubmed, since the API and the web interface have different rule expansion algorithms and return slightly different results [@pubmedUpdate].
A short guide on how to set up the framework for each supported database is available in Supplemental Material S3.\
The acquired records are merged into a single database, resolving duplicates and different formatting between sources.
The records are ordered according to the frequency of the positive query terms (e.g., not preceded by a $NOT$ modifier) in the title and abstract ("simple query ordering").\
The researcher is then asked to label a number of records to create the "initial training set" needed to start the automatic classification.
We suggest manually labelling the first 250 records (see "hyperparameter optimization" later).
The simple query ordering increases the positivity rate in the initial training set [@wallace2010active], which provide higher sensitivity during automatic classification [@chawla2004special].

@@

The collected citation data have a number of fields characterising a scientific publication.
The framework models the relevance of a record based on the following fields:
title, abstract, authors, keywords, MESH terms [@lipscomb2000medical].
A series of Natural Language Processing (NLP) techniques [@baeza1999modern; @marshall2015systematic; @ananiadou2006text] are employed to transform the textual information in these fields into features for machine learning through a bag-of-words approach [@marshall2015systematic].
The processing of free text fields (title, abstract) includes: tokenization (i.e., extracting the terms), common stopwords (i.e., sentence components bringing no meaning) removal, part-of-speech filtering (only nouns, adjectives, verbs and untagged terms are retained), and lemmatization of the terms (i.e., reduction to their base grammar form).
Text processing for authors, keywords and MESH terms identifies logical units (e.g., author's full names, composite keywords) and extracts them.\
Terms appearing in less than 5% of the labelled documents are removed from negative records.
All terms in the positive set are kept to increase sensitivity at the cost of specificity.\
Some terms tend to co-appear in records (non-consecutive ngrams, nc-ngrams), often carrying a particular meaning when copresent.
To detect nc-ngrams, we generated a word network representation [@rousseau2015graph] posing edges between terms with a cosine similarity in terms of record co-occurrence > 0.5.
We extracted the maximal cliques in the network [@eppstein2010listing] representing highly correlated groups of terms;
These groups of terms are added to the data set as individual features.
Only nc-ngrams comprising a maximum of ten terms are kept.\
A second network is built using a co-occurrence threshold of 0.9.
In this case, the cliques represent terms that always appear together and therefore can be considered redundant (i.e., they do not need to be considered separately).
These terms are merged to increase computation efficiency and reduce overfitting.\
The output is a Document-Term Matrix (DTM), with $N_d$ rows representing the records ($D_i$), $N_t$ terms column for the $t_{field}$ terms (divided by record field) and ${0,1}$ values whether $t_{field} \in D_i$.
We also enriched the DTM with features referencing the number of terms in each field to help the model scale term importance based on the field length.

@@

To assign the labels, we employed an "active learning" [@settles2009active, @miwa2014reducing] approach, where a human reviews a specific subset of predictions made from the machine, which is then retrained on the manually reviewed data set.
This process proceeds iteratively, decreasing prediction uncertainty.\
Label assignment is done through the identification of an "uncertainty zone" whose construction is possible thanks to the Bayesian nature of BART, which provides full PPDs instead of point-wise predictions for each record.\
To describe the process formally, we define

@@

## Relevant term extraction

@@

Since the algorithm is data-driven, it creates queries that effectively select positive records from the input data set but may be not specific enough once applied to actual research databases.
Therefore we appended an extra subquery in $AND$, which specifies the general topics of our search and delimitates the search domain.\
The new query was used to initiate a second search session.

@@

We trained a simple Bayesian logistic regression (surrogate model) on the reviewed records to evaluate the classification model consistency (see Discussion for the theoretical justification).
The surrogate model uses as predictor the lower bound of the 98% PrI of the records' PPD with weakly regularizing, robust priors for the intercept (Student T with $\nu=3,\mu=0,\sigma=2.5$) and the linear coefficient (Student T with $\nu=3,\mu=0,\sigma=1.5$).\
The quality of the model was evaluated through Bayesian $R^2$ [@gelman2019r], of which we reported the posterior median and 90% Credible Interval [90% CrI].
The $R^2$ also provides an evaluation of the consistency of the original classification model.
Given that this model is conditional only on the BART predictions and not on the DTM, it is characterized by more uncertainty, providing plausible worst-case scenarios.\
The surrogate model is then used to generate the predictive cumulative distribution of the number of total positive records in the whole data set.
This distribution allows estimating the expected total posterior "Sensitivity" and "Efficiency" of the classification model in the full (unreviewed) data set.
Efficiency is summarised by the "Work saved over random" (WSoR) statistic:
one minus the ratio between the number of record manually reviewed and those that would be required to find the same number of positives if classification was performed choosing records randomly;
this last quantity is estimated through a negative hypergeometric distribution [@chae1993presenting] over the predicted amount of positive records.\
For the number of predicted positive records, the sensitivity and the efficiency, we reported the "truncated 90% PrI" [trunc. 90% PrI], which is the uncertainty interval bounded at the number of observed total positive records (i.e., there cannot be less predicted positive records than observed).

@@

To evaluate the hyperparameter effect of performance, we set up a "grid search" [@claesen2015hyperparameter; @yang2020hyperparameter] on a prelabelled "validation set" made of the first 1200 records from the first session data set.
The framework tested each hyperparameter combination until four CR iterations with no positive records were returned or the whole data set got labelled.\
For each combination, a performance score was computed as the product of "Efficiency" (1 minus the ratio of records that required review over the total) and "Sensitivity" (number of positive records found over the total of positives).
We then identified homogeneous "performance clusters" of scores given hyperparameter values using a partition tree [@rpart].
For the rest of the study, we used the best hyperparameter set in terms of Sensitivity followed by Efficiency from the cluster with the highest average score.

### 2021-12-07 Manuscript/Manuscript_Results.Rmd
update
including Tjibbe's review

---
title: "Results"
date: "`r lubridate::today()`"
output:
  pdf_document:
    includes:
      in_header: header.tex
  github_document: default
---

@@

The input search query for the first session was:\

@@

The first search session returned a total of `r all_records` unique records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the EMBASE database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE (Table 1).
There were various degrees of overlapping between sources, with the `r percent(1 - source_distr[1])` of records being present in more than one database and EMBASE and IEEE being the databases with the higher uniqueness ratios.
The final dataset was composed by `r source_summary$Total$Records` unique records.\
The first `r num_first_labeling` records were manually labeled.
Of these `r sprintf('%d (%s)', num_first_positives, percent(num_first_positives/num_first_labeling))` were labeled as positive, and `r sprintf('%d (%s)', num_first_negatives, percent(num_first_negatives/num_first_labeling))` as negative.

`r print_table(search_results, caption = "**Table 1**. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. SAll session shows records after joining and deduplication of the Session 1 and Session 2 dataset.")`

@@

`r print_table(annotation_results, caption = "**Table 2**. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported.\"Unlab.\" indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.")`

By evaluating how often a term was used by the classification model, it is possible to define their relevance in labeling the records (see Methods).
Here follows the 15 most relevant terms by inclusion rate over 10,000 posterior tree inclusions, described as:
Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic].

@@

The "&" indicates nc-ngrams, i.e., terms strongly co-occurrent in the documents.\
The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
It is interesting to see that some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
these are terms which are relevant only together with other terms but not by themselves, highlighting the extra predictive power brought by a non-linear model like BART.\
A more extensive set of terms is presented in Table 1 of Supplemental Material S2.

@@

<!-- develop more in the methods, the data is not a random sample and it's ordered so performance evaluation needs to take this into account. also note that hyperparameter selection is necessary since even if bayesian methods are robust, the other parameters outside it are not-->

@@

`r print_table(perf_table, caption = '**Table 3**. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Work saved over random" (WSoR) are reported, with their 90% PrI truncated to a number of positive matches equal to the observed one. Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported. [PrI] represents the 90% Predictive Interval while [trunc. PrI] indicate the residual PrI truncated at the observed realization (see. methods).')`

```{r performance plot, cache = FALSE, fig.width=12, fig.height=5, fig.cap="**Figure 2**. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}

>>>>

---
title: "Results"
date: "`r lubridate::today()`"
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
  github_document: default
---

@@

The initial search query for the example topic was:\

@@

The first search session returned a total of `r all_records` unique records, specifically `r source_summary$Embase$Records` (`r source_summary$Embase$Perc_over_total` of the total) records from the EMBASE database, followed by `r source_summary$Pubmed$Records` (`r source_summary$Pubmed$Perc_over_total`) from Pubmed, `r source_summary$Scopus$Records` (`r source_summary$Scopus$Perc_over_total`) from SCOPUS, `r source_summary$WOS$Records` (`r source_summary$WOS$Perc_over_total`) from WOS, and `r source_summary$IEEE$Records` (`r source_summary$IEEE$Perc_over_total`) from IEEE (Table 1).
There were various degrees of overlapping between sources, with the `r percent(1 - source_distr[1])` of records being present in more than one database and EMBASE and IEEE being the databases with the higher uniqueness ratios.
The final data set was composed by `r source_summary$Total$Records` unique records.\
The first `r num_first_labeling` records (based on "simple query ordering") were manually labeled.
Of these `r sprintf('%d (%s)', num_first_positives, percent(num_first_positives/num_first_labeling))` were labeled as positive, and `r sprintf('%d (%s)', num_first_negatives, percent(num_first_negatives/num_first_labeling))` as negative.

`r print_table(search_results, caption = "**Table 1**. Distribution of retrieved records by source and session. For each source it is reported the number of records, percentage over the session total (after removing duplicates)' and, number or records specific for a source as absolute value and as percentage over the source total. All session shows records after joining and deduplication of the Session 1 and Session 2 data set.", label = "Table 1")`

@@

`r print_table(annotation_results, caption = "**Table 2**. Results of the automatic classifaction and manual review rounds. For each iteration, the cumulative number of positives and negative records and their sum (Total labelled) and percentage over total are shown. Also, the number of changes after review and their description is reported.\"Unlab.\" indicates unlabelled records marked for review. For each Iteration, also the number of features used by the engine is reported. The first row reports the results of the initial manual labelling of records, which acted as input for the automatic classification in Iteration 1. In Session 2, the engine uses the labels at the end of Session 1 to classify the newly added records.", label = "Table 2")`

By evaluating how often a term was used by the classification model, it is possible to define their relevance in labeling the records (see Methods).
Here follows the 15 most relevant terms by inclusion rate over 10,000 posterior tree, described as:
Term (citation part): Inclusion Rate (Inclusion Stability) [linear Relative Risk, Statistic].

@@

The "&" indicates nc-ngrams, i.e., terms strongly co-occurrent in the documents.\
The engine was able to pick up the central concept of the research, i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections, and even one of the authors of this study (Donker T.) as well as the region of interest ("Orange County") of another research group active on the topic of healthcare asociated pathogen spreading over hospital networks.
It is interesting to see that some terms were considered highly relevant for the BART models (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model their effect would be hardly significant (statistic: -1.21 s.e.);
these are terms which are relevant only together with other terms but not by themselves, highlighting the extra predictive power brought by a non-linear model like BART.\
A more extensive set of terms is presented in Table 1 of Supplemental Material S2.

@@

@@

`r print_table(perf_table, caption = '**Table 3**. Estimated performance summary. The table reports for each session, the number of reviewed records and the percentage over the total. Also, the posterior expected number of positive records, "Sensitivity" and "Efficiency" (as WSoR) are reported, with their 90% PrI truncated to the observed realization in the dataset [trunc. PrI] (see. methods). Finally the median Bayesian $R^2$ [90% CrI] of the logistic models is reported. PrI: Predictive Intervals; CrI: Credibility Intervals', allow_math = TRUE, label = "Table 3")`

```{r performance plot, cache = FALSE, fig.width=6, fig.height=2.5, fig.cap="**Figure 2**. Observed cumulative number of positive matches (red dots) sorted by simple query ordering. The [trunc. 90% PrI] of the cumulative positive matches estimated by the logistic Bayesian model is shown as shaded area delimited by the 95% quantile of the PrI and by the observed number of positive matches (light blue lines). The median of the PrI is represented by a darker blue line."}
